Predicting Kamala Harris's Victory in the 2024 US Election

### 2024-11-02 paper/paper.qmd
Modify Estimand

## Estimand
In this analysis, the estimand is the true effect of polling factors on the projected support for Trump and Harris in the 2024 U.S. election. Specifically, this effect encompasses how variables like poll quality, transparency, sample size, and timing influence predicted vote percentages for Kamala Harris and Donald Trump across states. This build-up of estimand ensures consistency by clarifying that our target effect is the overall impact of these factors on candidates’ state-by-state electoral prospects. The estimand guides the model design and interpretation to achieve our goal of predicting the election outcome.

>>>>

In this analysis, the estimand is the true effect of polling factors on projected support for Trump and Harris in the 2024 U.S. election. Specifically, it reflects how variables such as poll quality, transparency, sample size, and timing influence the predicted vote percentages for Kamala Harris and Donald Trump across states. Defining the estimand clearly ensures consistency in the analysis by guiding model design and interpretation, preventing unintended shifts in focus due to minor methodological changes.
